\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-22 main.Rmd

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating till mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 3pm for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 6pm on week days.

@@

Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households. Figure \ref{fig:h12} and \ref{fig:h34} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their week day energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

```{r h12, fig.height = 10, fig.cap = "Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June."}
```

```{r h34, fig.height = 10, fig.cap = "Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating."}
```

>>>>

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating till mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 3pm for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 6pm on week days. Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

Figure \ref{fig:h12} and \ref{fig:h34} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their week day energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

```{r h1, fig.height = 5, fig.cap = "Calendar displays for household 1. They tend to use air conditioning in the late afternoon untill the mid-night in summer. It seems that they are on vacation in June."}
```

```{r h2, fig.height = 5, fig.cap = "Calendar displays for household 2. It reveals their regular tendency of using air conditioning and heating, and vacation periods. They leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June."}
```

```{r h3, fig.height = 5, fig.cap = "Calendar displays for household 3. Their energy use reveals different behaviors between summer and winter: only one peak in most summer days, while two peaks in winter. They are on long trips twice in the past year."}
```

```{r h4, fig.height = 5, fig.cap = "Calendar displays for household 4. Energy are heavily used in the evening for household 4. They also take three short trips in October, December, and June."}
```

### 2018-10-22 main.tex

\section{Introduction}\label{introduction}

@@

\section{Creating a calendar display}\label{creating-a-calendar-display}

@@

\subsection{Data transformation}\label{data-transformation}

@@

\subsection{Options}\label{options}

@@

\subsubsection{Layouts}\label{layouts}

@@

\subsubsection{Polar transformation}\label{polar-transformation}

@@

\subsubsection{Scales}\label{scales}

@@

\subsubsection{Orientation}\label{orientation}

@@

\subsubsection{Language support}\label{language-support}

@@

\subsection{Variations}\label{variations}

@@

\subsubsection{Overlaying and faceting
subsets}\label{overlaying-and-faceting-subsets}

@@

\subsubsection{Different types of plots}\label{different-types-of-plots}

@@

\subsubsection{Interactivity}\label{interactivity}

@@

\section{Case study}\label{case-study}

@@

Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical
toolkit, are useful for summarizing overall deviations across days and
households. Figure \ref{fig:h12} and \ref{fig:h34} display the data in
calendar layout individually for each household, unfolding their
day-to-day life. Glancing through Figure \ref{fig:h12}, their week day
energy use distinguishes from their weekends. We can exactly tell when
their air conditioner and heater are turned on. Heating keeps
functioning in consecutive hours at household 2, which is evident in the
mid July; while household 1 uses them cautiously. This finding helps
explain the strips and clusters in Figure \ref{fig:hod}. The calendar
plots speak the stories about vacation time that are untold by previous
figures. Household 1 is on vacation over three weeks of June, and
household 2 was also away for holidays during Christmas and the second
week of June. Figure \ref{fig:h34} shows household 3 takes two
one-month-long family trips in September till early October and in
June/July, and household 4 is away over two or three weeks in early
October, December and late June. The use of air conditioning and heating
leaves no trace in these two households.

@@

\caption{Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating.}\label{fig:h34}
\end{figure}

\section{Discussion}\label{discussion}

@@

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

>>>>

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{creating-a-calendar-display}{%
\section{Creating a calendar
display}\label{creating-a-calendar-display}}

@@

\hypertarget{data-transformation}{%
\subsection{Data transformation}\label{data-transformation}}

@@

\hypertarget{options}{%
\subsection{Options}\label{options}}

@@

\hypertarget{layouts}{%
\subsubsection{Layouts}\label{layouts}}

@@

\hypertarget{polar-transformation}{%
\subsubsection{Polar transformation}\label{polar-transformation}}

@@

\hypertarget{scales}{%
\subsubsection{Scales}\label{scales}}

@@

\hypertarget{orientation}{%
\subsubsection{Orientation}\label{orientation}}

@@

\hypertarget{language-support}{%
\subsubsection{Language support}\label{language-support}}

@@

\hypertarget{variations}{%
\subsection{Variations}\label{variations}}

@@

\hypertarget{overlaying-and-faceting-subsets}{%
\subsubsection{Overlaying and faceting
subsets}\label{overlaying-and-faceting-subsets}}

@@

\hypertarget{different-types-of-plots}{%
\subsubsection{Different types of
plots}\label{different-types-of-plots}}

@@

\hypertarget{interactivity}{%
\subsubsection{Interactivity}\label{interactivity}}

@@

\hypertarget{case-study}{%
\section{Case study}\label{case-study}}

@@

Figure \ref{fig:h12} and \ref{fig:h34} display the data in calendar
layout individually for each household, unfolding their day-to-day life.
Glancing through Figure \ref{fig:h12}, their week day energy use
distinguishes from their weekends. We can exactly tell when their air
conditioner and heater are turned on. Heating keeps functioning in
consecutive hours at household 2, which is evident in the mid July;
while household 1 uses them cautiously. This finding helps explain the
stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak
the stories about vacation time that are untold by previous figures.
Household 1 is on vacation over three weeks of June, and household 2 was
also away for holidays during Christmas and the second week of June.
Figure \ref{fig:h34} shows household 3 takes two one-month-long family
trips in September till early October and in June/July, and household 4
is away over two or three weeks in early October, December and late
June. The use of air conditioning and heating leaves no trace in these
two households.

@@

\caption{Calendar displays for household 2. It reveals their regular tendency of using air conditioning and heating, and vacation periods. They leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June.}\label{fig:h2}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h3-1}

\caption{Calendar displays for household 3. Their energy use reveals different behaviors between summer and winter: only one peak in most summer days, while two peaks in winter. They are on long trips twice in the past year.}\label{fig:h3}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h4-1}

\caption{Calendar displays for household 4. Energy are heavily used in the evening for household 4. They also take three short trips in October, December, and June.}\label{fig:h4}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}
